### 2021-09-21 documentos/pce.tex

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

>>>>

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\left\{ \frac{1}{2^{N/2}}\sigma_{\vec
\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $1/2^{N/2} \left\{\sigma_{\vec \alpha} \right\}_{\vec \alpha}$
 \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.
